Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-01-20 paper/rei.tex

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_tanh_highz_kde_f0p14_tau_z_to_zstart_plot_tau_gtz_dz0p1.pdf}
\caption{The 68\% and 95\% C.L. constraints on the cumulative optical depth $\tau(z, \zmax)$ for the two-step model, which allows for high-redshift ionization up to $\zmax =30$. note that a physical model with $\tau(15, \zmax) = 0.02$ is still allowed at the 95\% C.L. whereas the Planck FlexKnot analysis would have ruled it out with their $\tau(15, \zmax) < 0.007$ 95\% upper limit. [add not PC filtered version]
}
\label{fig:plot_taugtz_two_step_contours}
\end{figure}

@@

 \begin{figure}
          \includegraphics[width=0.9\columnwidth]{paper/plots/pl18_pc_zmax30_pliklite_srollv2_plot_rotated_box_flat_tau_prior_fac_0.8.png}
          \caption {Priors on the $m_1-m_2$ parameter space: the physicality prior (inset square, solid lines) and a flat prior in
          both $\tau_{12}$ and $m_1-m_2$ (rotated rectangle, dashed lines) which are aligned with lines of constant $\tau_{12}$ (light gray lines). Note that although the physicality prior allows for more parameter space at higher $\tau_{12}$, that is also the region excluded by the data constraints (ellipses). The only difference in the allowed region is that the physicality prior clips the low $m_1$ portion of the allowed region due to the physicality condition and the assumption that reionization occurs at $z\ge 6$.} 
          \label{fig:prior_box}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_taugtz_tanh_highz_direct_vs_kde_vs_gaussian_dz_auto_zre_prior_6p1.pdf}
\caption{The 68\% and 95\% C.L. constraints on the cumulative optical depth $\tau(z, \zmax)$ for the two-step model, which allows for high-redshift ionization up to $\zmax =30$. note that a physical model with $\tau(15, \zmax) = 0.02$ is still allowed at the 95\% C.L. whereas the Planck FlexKnot analysis would have ruled it out with their $\tau(15, \zmax) < 0.007$ 95\% upper limit. [add not PC filtered version]
}
\label{fig:plot_taugtz_two_step_contours}
\end{figure}

@@

 \begin{figure}
          \includegraphics[width=0.9\columnwidth]{paper/plots/pl18_pc_zmax30_pliklite_srollv2_1015_plot_rotated_box_flat_tau_prior_fac_0.8.pdf}
          \caption {Priors on the $m_1-m_2$ parameter space: the physicality prior (inset square, solid lines) and a flat prior in
          both $\tau_{12}$ and $m_1-m_2$ (rotated rectangle, dashed lines) which are aligned with lines of constant $\tau_{12}$ (light gray lines). Note that although the physicality prior allows for more parameter space at higher $\tau_{12}$, that is also the region excluded by the data constraints (ellipses). The only difference in the allowed region is that the physicality prior clips the low $m_1$ portion of the allowed region due to the physicality condition and the assumption that reionization occurs at $z\ge 6$.} 
          \label{fig:prior_box}
\end{figure}
